Notes

### 2020-03-30 Notes/Notes.tex
ground states normalization in notes

The probability to get the ground state at measurement is
\begin{align}
P =\sum_i | \langle \psi (t)  | \mbox{gnd}_i \rangle |^2 ,
\end{align}
where the summation runs over degenerated ground states.

@@

The probability to get the ground state at measurement is
\begin{align}
P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
\end{align}
where the projection operator onto the ground state subspace is $\pi_{\mbox{gnd}}=\sum_i |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.

>>>>

The probability to get the ground state at measurement is
\begin{align}
P =\sum_{i\in G} | \langle \psi (t)  | \mbox{gnd}_i \rangle |^2 ,
\end{align}
where $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace.

@@

The probability to get the ground state at measurement is
\begin{align}
P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
\end{align}
where the projection operator onto the degenerated ground states subspace is $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
